Modularizing Street Map Generation \\ \vspace{8pt} \large An Adventure in Tensors

### 2013-12-12 paper/paper.tex

\begin{abstract}
\end{abstract}

>>>>

\begin{abstract}
This paper addresses the issue of creating modular, extensible code given an
existing solution to a problem, namely, interactively modeling large street
networks. We describe an implementation in Haskell of a framework that allows 
users to create a street network from scratch, based on the techniques described 
in [Chen]. In particular, we were able to express the underlying mathematics
more intuitively that is possible in an imperative language.

\end{abstract}
